---
title: "Organise Your Dailies"
author: "Alice de Sampaio Kalkuhl"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/alice/Documents/GitHub/Genshin')
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results='asis')
library(tidyverse)
library(purrr)
library(rmarkdown)
library(gtools)
library(DT)
library(tableHTML)
rmd_tabsets <- function(.data) {

  # first empty header to intialize tabsets
  cat("#### { .tabset .unlisted .unnumbered}", "\n\n", sep = "")

  purrr::imap(.data, function(.x, .y) {
    cat("##### TEAM ", .y, "\n\n", sep = "")
    print(tableHTML::tableHTML(.x, border = 0))
    cat("\n\n")
  })
  # close with empty header to stop tabsets
  cat("#### {.unlisted .unnumbered}")
}
```
## Who do you have?
Your characters and their constellations matter a lot for what you need to do. 

Here, you will need a table with your characters, how often you pulled them, and how you plan on using them. 

We are going to set a couple of conditions for characters to give them priorities. If you don't want to play a character, don't use it. 

## Ascension materials
I prepared a table based on the Genshin Wiki on which [ascension materials](https://genshin-impact.fandom.com/wiki/Character_Ascension_Material) characters need. [Level up materials](https://genshin-impact.fandom.com/wiki/Character_Level-Up_Material) and [specialties](https://genshin-impact.fandom.com/wiki/Local_Specialty) also have to be farmed. Out of all the materials, the specialities scale the most and might be the most difficult to farm. They can't be crafted and the shops that carry them only have 5 at a time. For example, as a Layla main, I spend much more time looking for [Nilotalpa Lotuses](https://gamewith.net/genshin-impact/article/show/34257) than defeating her boss or farming for her talents which is why I put an extra point of priority on the specialities


```{r}
level_up_materials <- read.csv("character_materials.csv") %>% 
  separate_rows(character,sep=' & ')
local_specialties <- read.csv("local_specialties.csv") %>% separate_rows(character,sep=' & ')
all_characters <- read.csv("all_characters.csv") %>% group_by(element) %>% mutate(element_score=n()) %>% ungroup()
characters <- purrr::reduce(list(all_characters,level_up_materials,local_specialties), dplyr::left_join, by = "character") %>% mutate(ascension = case_when(
  element == "Traveler" ~ "Brilliant Diamond",
  element == "Pyro" ~ "Agnidus Agate",
  element == "Hydro" ~ "Varunada Lazurite",
  element == "Dendro" ~ "Nagadus Emerald",
  element == "Electro" ~ "Vajrada Amethyst",
  element == "Anemo" ~ "Vayuda Turquoise",
  element == "Cryo" ~ "Shivada Jade",
  element == "Geo" ~ "Prithiva Topaz")) 
```
You can also buy materials in game but I haven't included where, because I can't in good conscience recommend spending your mora and starglitter like this. Here, we also rank the characters by their usage to prioritise farming. My personal ranking is: 

|style|rank|
|---|---|
|Unused|0|
|TBD|1|
|Exploration|2|
|Finisher|3|
|Healer|4|
|Support|5|
|Shielder|6|
|DPS|7|

```{r conditions for which characters to Farm for characters}
my_characters <- read.csv("my_characters.csv", header = T,row.names = NULL) %>% 
                  mutate(faves_priority=case_when(style == "Unused" ~ 0,
                                                  style == "TBD" ~ 1,
                                                  style == "Exploration" ~ 2,
                                                  style == "Finisher" ~ 3,
                                                  style == "Healer" ~ 4,
                                                  style == "Support" ~ 5,
                                                  style == "Shielder" ~ 6,
                                                  style == "DPS" ~ 7,
                                                  style == "Main" ~ 8))
# names(my_characters) <- c("pulls","character","style") run this, if you named the variables different in your table
farming <- merge(my_characters,characters,on="character") %>% 
  filter(pulls > 0 & style != "TBD" & style != "Unused") # let's only farm for characters you have and want to be using 
```

```{r prepare your pulls,echo=FALSE}
wishlist <- left_join(my_characters,all_characters,by="character") %>% filter(pulls==0) %>% pull(character)
wishlist
```

# Bosses 
Here is a list of all bosses you need. I would recommend farming bosses that you need more than 1 
```{r bosses,echo=FALSE}
farming_bosses <- farming %>% 
  group_by(source,material) %>% 
  mutate(boss_score=n()) %>%
  ungroup()
```


# Local Specialities 
```{r local specialties, echo=FALSE}
local_farming <- farming_bosses %>% 
                  select(character,local_specialty,location) %>% 
                  distinct() %>% 
                  group_by(local_specialty) %>% 
                  mutate(local_score=n()) %>% 
                  ungroup()
```

```{r prioritise your farming}
farming_sorted <- left_join(local_farming,farming_bosses,by=c("character","local_specialty","location")) %>% 
                    mutate(farming_priority=local_score+boss_score+faves_priority) %>% 
                    select(character,local_specialty,location,source,material,farming_priority) %>% 
                    group_by(character) %>% 
                    mutate(boss = paste(source,collapse = " & "),
                           boss_material = paste(material,collapse = " & ")) %>% 
                    select(-c(source,material)) %>% 
                    relocate(farming_priority, .after=character) %>% arrange(-farming_priority) %>% distinct()
paged_table(farming_sorted)
```


# Preparing Talents 
For example, Alhaitham will be available soon. Now, the trial will give you ascension materials to level him until level 40 but you still need to unlock his boss. One thing that is much easier to unlock is to get his talents to level 2, so that's what we're doing here. Talent domains are accessible on specific days. 



# Team Construction
It's time to build teams with what we have. 

There are a couple of unintuitive things. For example, I main Layla and I've run into a couple of problems. In a Freeze Teak, playing a Claymore character will break the Freeze and as an extra yikes unless you want shatter. 

I've tried Jean once and she needs at least 1 Catalyst or Bow chaeacters in her team, because she spreads the opponents ridiculously far out. g

```{r teams, echo=FALSE}
team_df <- merge(my_characters,characters,on="character") %>%
filter(pulls > 0) %>% 
group_by(character,style,element,weapon,region) %>% tally() %>% select(-n)
teams_characters <- combinations(length(team_df$character),4,team_df$character,repeats.allowed = FALSE) %>% as.data.frame()
teams <- list()
for (i in 1:nrow(teams_characters)){
  team <- as.vector(teams_characters[i,])
  this_team <- team_df %>% 
    filter(character %in% team)
  teams[[i]] <- this_team
}

combat_teams <- teams %>% discard(.,~ "Exploration" %in% .x$style | "Expedition" %in% .x$style | "Unused" %in% .x$style) 
combat_teams <- combat_teams %>% discard(., ~ "Alhaitham" %in% .x$character & !("Kaveh" %in% .x$character) & !("Hydro" %in% .x$element) & !("Electro" %in% .x$element))
combat_teams <- combat_teams %>% discard(., ~ "Charlotte" %in% .x$character & !("Fontaine" %in% .x$region))
combat_teams <- combat_teams %>% discard(., ~ "Chiori" %in% .x$character & length(grep("Anemo",.x$element)) < 3)
combat_teams <- combat_teams %>% discard(., ~ "Emilie" %in% .x$character & !("Pyro" %in% .x$element))
combat_teams <- combat_teams %>% discard(., ~ "Faruzan" %in% .x$character & length(grep("Anemo",.x$element)) < 3)
combat_teams <- combat_teams %>% discard(., ~ "Gaming" %in% .x$character & !("Anemo" %in% .x$element))
combat_teams <- combat_teams %>% discard(., ~ "Kaveh" %in% .x$character & !("Alhaitham" %in% .x$character) & !("Hydro" %in% .x$element))
combat_teams <- combat_teams %>% discard(., ~ "Lynette" %in% .x$character & length(grep("Anemo",.x$element)) > 2 | "Lynette" %in% .x$character & length(grep("Geo",.x$element)) > 2 | "Lynette" %in% .x$character & length(grep("Anemo",.x$element))+ length(grep("Geo",.x$element)) > 2)
combat_teams <- combat_teams %>% discard(., ~ "Nilou" %in%  .x$character & "Electro" %in% .x$element | "Nilou" %in%  .x$character & "Anemo" %in% .x$element | "Nilou" %in%  .x$character & "Geo" %in% .x$element | "Nilou" %in%  .x$character & "Pyro" %in% .x$element | "Nilou" %in%  .x$character & "Cryo" %in% .x$element | "Nilou" %in%  .x$character & "Electro" %in% .x$element & length(grep("Dendro",.x$element)) < 1)
combat_teams <- combat_teams %>% discard(., ~ "Shenhe" %in% .x$character & length(grep("Cryo",.x$element))<2)
combat_teams <- combat_teams %>% discard(., ~ "Sangonomiya Kokomi" %in% .x$character & "Dendro" %in% .x$element)
combat_teams <- combat_teams %>% discard(., ~ "Sayu" %in% .x$character &  length(grep("Anemo",.x$element))>1 | "Sayu" %in% .x$character &  length(grep("Cryo",.x$element))>1 | "Sayu" %in% .x$character &  length(grep("Dendro",.x$element))>1 |  "Sayu" %in% .x$character &  length(grep("Electro",.x$element))>1 | "Sayu" %in% .x$character &  length(grep("Geo",.x$element))>1 | "Sayu" %in% .x$character &  length(grep("Hydro",.x$element))>1 | "Sayu" %in% .x$character &  length(grep("Pyro",.x$element))>1)
combat_teams <- combat_teams <- combat_teams %>% discard(., ~ "Sucrose" %in% .x$character & length(grep("Anemo",.x$element)) > 2 | "Sucrose" %in% .x$character & length(grep("Geo",.x$element)) > 2 | "Lynette" %in% .x$character & length(grep("Anemo",.x$element)) + length(grep("Geo",.x$element)) > 2)
```

## Freeze 
We need Cryo and Hydro for a Freeze team. Also, I prefer to permafreeze, so we will be excluding Claymore and Pyro users. 

```{r freeze team,echo=FALSE}
freeze_teams <- discard(combat_teams, ~ "Pyro" %in% .x$element | "Claymore" %in% .x$weapon | "Unused" %in% .x$style)
my_freeze_team <- discard(freeze_teams, ~ !("Hydro" %in% .x$element))
my_freeze_team <- discard(my_freeze_team, ~ !("Cryo" %in% .x$element))
rmd_tabsets(my_freeze_team)
```

## Hyperbloom
There are no negative conditions to Hyperbloom but we need a Hydro, a Dendro, and an Electro character. 

```{r hyperbloom team,echo=FALSE}
hyperbloom_teams <- keep(teams, ~ "Dendro" %in% .x$element & "Hydro" %in% .x$element & "Electro" %in% .x$element)
my_hyperbloom_team <- discard(hyperbloom_teams, ~ "Unused" %in% .x$style | "Exploration" %in% .x$style) 
rmd_tabsets(my_hyperbloom_team)
```

# Exploration 
If you want to optimise your teams, bring a Pyro character for all your exploration quests to light torches. Remember to bring a bow character too.


```{r exploration teams,echo=FALSE}
exploration_teams <- teams # %>% keep(., ~ "Pyro" %in% .x$element & "Bow" %in% .x$weapon)
```

Personally, I prefer to take characters from a Region to explore the region.

## Mondstadt 
We also need an Anemo and Electro characters for puzzles here. Remeber to only bring characters you want to bring. 

```{r Mondstadt exploration,echo=FALSE}
Mondstadt <- keep(exploration_teams, ~ "Mondstadt" %in% .x$region & "Anemo" %in% .x$element & "Electro" %in% .x$element)  
my_Mondstadt_exploration <- discard(Mondstadt, ~ "Unused" %in% .x$style) %>% discard(., ~ "Unused" %in% .x$style) %>% discard(., ~ "Liyue" %in% .x$region) %>% discard(., ~ "Inazuma" %in% .x$region) %>% discard(., ~ "Sumeru" %in% .x$region) %>% discard(., ~ "Fontaine" %in% .x$region)
rmd_tabsets(my_Mondstadt_exploration)
```

## Liyue
We will need a Geo character here. 

```{r Liyue exploration team,echo=FALSE}
my_Liyue_exploration <-exploration_teams %>% keep(., ~ "Liyue" %in% .x$region & "Geo" %in% .x$element & "Yanfei" %in% .x$character) %>% discard(., ~ "Unused" %in% .x$style) %>% discard(., ~ "Mondstadt" %in% .x$region) %>% discard(., ~ "Inazuma" %in% .x$region) %>% discard(., ~ "Sumeru" %in% .x$region) %>% discard(., ~ "Fontaine" %in% .x$region)
rmd_tabsets(my_Liyue_exploration)
```

## Inazuma
We will need at least one Electro character here. 

```{r Inazuma exploration, echo=FALSE} 
my_Inazuma_exploration <- exploration_teams %>% keep(., ~ length(grep("Inazuma",.x$region))==4 & "Electro" %in% .x$element) %>% discard(., ~ "Unused" %in% .x$style) %>% discard(., ~ "Mondstadt" %in% .x$region) %>% discard(., ~ "Liyue" %in% .x$region) %>% discard(., ~ "Sumeru" %in% .x$region) %>% discard(., ~ "Fontaine" %in% .x$region)
rmd_tabsets(my_Inazuma_exploration)
```

## Sumeru Forest 
```{r Sumeru Forest exploration, echo=FALSE}
my_Sumeru_forest_exploration <- exploration_teams %>% keep(., ~ "Sumeru" %in% .x$region & "Dendro" %in% .x$element & "Electro" %in% .x$element & "Tighnari" %in% .x$character) %>% discard(., ~ "Unused" %in% .x$style) %>% discard(., ~ "Mondstadt" %in% .x$region) %>% discard(., ~ "Liyue" %in% .x$region) %>% discard(., ~ "Inazuma" %in% .x$region) %>% discard(., ~ "Fontaine" %in% .x$region)
rmd_tabsets(my_Sumeru_forest_exploration)
```
 
## Sumeru Desert 
For the desert, we should bring Dendro and Anemo in addition to our Pyro character. 

```{r Sumeru desert exploration, echo=FALSE}
my_Sumeru_desert_exploration <- keep(exploration_teams, ~ "Sumeru" %in% .x$region & "Dendro" %in% .x$element) %>% keep(., ~ "Anemo" %in% .x$element & "Sethos" %in% .x$character) %>% discard(., ~ "Unused" %in% .x$style) %>% discard(., ~ "Mondstadt" %in% .x$region) %>% discard(., ~ "Liyue" %in% .x$region) %>% discard(., ~ "Inazuma" %in% .x$region) %>% discard(., ~ "Fontaine" %in% .x$region)

rmd_tabsets(my_Sumeru_desert_exploration)
```

## Fontaine
```{r Fontaine exploration, echo=FALSE} 
my_Fontaine_exploration <- keep(exploration_teams, ~ "Fontaine" %in% .x$region & "Hydro" %in% .x$element & "Clorinde" %in% .x$character) %>% discard(., ~ "Unused" %in% .x$style) %>% discard(., ~ "Mondstadt" %in% .x$region) %>% discard(., ~ "Liyue" %in% .x$region) %>% discard(., ~ "Inazuma" %in% .x$region) %>% discard(., ~ "Sumeru" %in% .x$region)
rmd_tabsets(my_Fontaine_exploration)
```
# Talents 
Now, this is a bonus but did check your characters talents recently? Levelling them up can be the difference between getting stuck on an Archon quest and cruising through. They are optional though, so if you prefer levelling up and farming bosses or collecting artifacts

```{r talents,echo=FALSE}
talents <- read.csv("talents.csv") %>% 
separate_rows(character,sep=' & ')

talent_farming <- merge(farming,talents,on="character") %>%       
separate_rows(days,sep=' & ')

farming_timed <- merge(farming_sorted,talent_farming,on="character") %>% 
select(character,farming_priority,boss,days,domain) %>% 
relocate(days,.after=farming_priority) %>% 
filter(days==wday(today(), label = TRUE))
paged_table(farming_timed)
```

# Artifacts
Do yourself a favour and skip this section, if your world level is lower than 5. When you build your characters, it is obviously up to you how you want to build them. Once you have decided, the following will help prioritise domains. 

```{r artifacts}
artifacts <- read.csv("artifacts.csv")
character_artifacts <- my_characters %>%
                    separate_rows(artifacts,sep =" & ")
artifact_farming <- merge(character_artifacts,artifacts,on="artifacts") %>%
                    group_by(artifact_location) %>% 
                    mutate(artifact_priority=n()) %>% 
                    ungroup() %>% select(character,artifacts,artifact_location,artifact_region,artifact_priority) %>% distinct()
paged_table(artifact_farming)
```
