---
title: "Organise Your Dailies"
author: "Alice de Sampaio Kalkuhl"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Who do you have?
Your characters and their constellations matter a lot for what you need to do. 

Here, you will need a table with your characters, how often you pulled them, and how you plan on using them. 

We are going to set a couple of conditions for characters to give them priorities. If you don't want to play a character, don't use it. 

## Ascension materials
I prepared a table based on the Genshin Wiki on which [ascension materials](https://genshin-impact.fandom.com/wiki/Character_Ascension_Material) characters need. 

Level up materials and 

[specialties](https://genshin-impact.fandom.com/wiki/Local_Specialty)


```{r}
level_up_materials <- read.csv("character_materials.csv") %>% 
  separate_rows(character,sep=' & ')
local_specialties <- read.csv("local_specialties.csv") %>% separate_rows(character,sep=' & ')
characters <- merge(level_up_materials,local_specialties,on="character") %>% mutate(ascension = case_when(
  element == "Traveler" ~ "Brilliant Diamond",
  element == "Pyro" ~ "Agnidus Agate",
  element == "Hydro" ~ "Varunada Lazurite",
  element == "Dendro" ~ "Nagadus Emerald",
  element == "Electro" ~ "Vajrada Amethyst",
  element == "Anemo" ~ "Vayuda Turquoise",
  element == "Cryo" ~ "Shivada Jade",
  element == "Geo" ~ "Prithiva Topaz")) # add element to "my_characters.csv

my_characters <- read.csv("my_characters.csv")
# names(my_characters) <- c("pulls","character","style") run this, if you named the variables different in your table
```

You can also buy materials in game but I haven't included where, because I can't in good conscience recommend spending your mora and starglitter like this.


 

```{r pressure, echo=FALSE}


```
All information taken from [here](https://genshin-impact.fandom.com/wiki/Character_Ascension_Material)


```{r conditions}
farming <- merge(my_characters,characters,on="character") %>% 
  filter()
```
